Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*

### 2020-06-07 paper.Rmd
I made some more cleanup
Please do anything you want with this over the weekend. I think we should try to get some feedback on it early next week, guys.

---
title: "Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*"
author: Andreas Beger, Richard K. Morgan, and Michael D. Ward
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  pdf_document:
    keep_tex: true
references:
- id: blair2020forecasting
  title: "Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning"
  author:
  - family: Blair
    given: Robert A.
  - family: Sambanis
    given: Nicholas
  container-title: Journal of Conflict Resolution
  type: article-journal
  issued:
    year: 2020
bibliography: 
  - "`r user <- Sys.info()[['user']]; if (user=='andybega')  '/Users/andybega/Work/whistle/master.bib' else if (user=='mdw') '/Users/mdw/Git/whistle/master.bib' else 'references.bib'`"
---

@@

@bdm:2011 , @ward:2016 , @montgomery:etal:PS:2012, @chiba:etal:2015, @brandt:2015  @mhw:2012,@ward:etal:2013,@chadefaux:2015,@weidmann:ward:2010,@pilster:bohmelt:2014,@Brandt_etal_2011,@gleditsch:2015,@bennett:stam:2009,@shellman:etal:2013,@hegre:etal:2011,@ward:etal:2010,@freeman:job:1979,@gneiting:raftery:2005
@choucri:1974,@choucri:robinson:1979,@goldstone:etal:2010,tetlock:etal:2017,
@rost:etal:2009,  
@hopple:andriole:1984,
@andriole:young:1977,
@brandt:etal:2011,
@brandt:etal:2014,
@mellers:etal:2015,
@tetlock:gardner:2015,
@hegre:etal:2019,
@weidmann:ward:2010, 
@beger:ward:2017,
@schrodt:1991,
@obrien:2010,
@obrien:2002,
@hegre:etal:2019,
@hegre:etal:2017,
@hegre:etal:2016,
@chiba:gleditsch:2017,
@buhaug:etal:2014,
@colaresi:mahmood:2017,
@ramakrishnan:etal:2014,
@schleussner:etal2016,
@kupilik:witmer:2018,
@witmer:etal:2017
@oloughlin:etal:2012
@hegre:etal:2013 
@buhaug:gleditsch:2008

**AB: add a table comparing B&S original claims and updated results.**

>>>>

---
title: "Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*"
author: 
 - Andreas Beger^[Predictive Heuristics, adbeger@gmail.com. corresponding author]
 - Richard K. Morgan^[World Bank, rick.morgan2@gmail.com]
 - Michael D. Ward^[Predictive Heuristics, Duke University, University of Washington, michael.don.ward@gmail.com]
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  pdf_document:
    keep_tex: true
references:
- id: blair2020forecasting
  title: "Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning"
  author:
  - family: Blair
    given: Robert A.
  - family: Sambanis
    given: Nicholas
  container-title: Journal of Conflict Resolution
  type: article-journal
  issued:
    year: 2020
bibliography: 
  - "`r user <- Sys.info()[['user']]; if (user=='andybega')  '/Users/andybega/Work/whistle/master.bib' else if (user=='mdw') '/Users/mdw/Git/whistle/master.bib' else 'references.bib'`"
---

@@

There is a fairly long tradition of making predictions in academic and policy work on conflict. Most of these are not mentioned by B&S.  We would include work from the last century including @choucri:1974, @andriole:young:1977, @choucri:robinson:1979, @freeman:job:1979,@hopple:andriole:1984, @schrodt:1991, and others. 
The current century has even more work that can't be overlooked or combined into a theory barren classification
@obrien:2002,
@buhaug:gleditsch:2008, 
@bennett:stam:2009,
@rost:etal:2009, 
@obrien:2010, 
@weidmann:ward:2010, 
@weidmann:ward:2010, 
@ward:etal:2010,
@goldstone:etal:2010, 
@bdm:2011, 
@brandt:etal:2011, 
@hegre:etal:2011, 
@Brandt_etal_2011, 
@oloughlin:etal:2012, 
@hegre:etal:2013, @shellman:etal:2013, 
@ward:etal:2013, 
@brandt:etal:2014, 
@buhaug:etal:2014, 
@ramakrishnan:etal:2014, 
@pilster:bohmelt:2014, 
@brandt:2015, @chadefaux:2015, 
@chiba:etal:2015, @gleditsch:2015, 
@mellers:etal:2015, 
@tetlock:gardner:2015, 
@hegre:etal:2016, 
@schleussner:etal2016, @ward:2016, 
@beger:ward:2017, 
@chiba:gleditsch:2017,
@colaresi:mahmood:2017, 
@hegre:etal:2017, 
@tetlock:etal:2017, 
@witmer:etal:2017, 
@kupilik:witmer:2018, 
@hegre:etal:2019, 
@hegre:etal:2019.
Indeed this scholarship has brought us to the point where predictive analysis of conflict studies is not unknown in the scholarly and policy arenas.  Most, if not all of these authors, would probably claim some theoretical motivation. The a-theoretical case is a counterfactual that either includes everything, or nothing, as aruged in @ward:2016. In the B&S article it serves as a strawman. Unfortunately for B&S that strawman outperforms there putatively theoretical model. Important statistical developments have also added to this research vector, including especially 
@gneiting:raftery:2005, 
@montgomery:etal:PS:2012, and
@mhw:2012.
